---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scriptR

<!-- badges: start -->

<!-- badges: end -->

The goal of scriptR is to parse R scripts into a format that is suitable for analysis.

## Installation

You can install the development version of `scriptR` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("acastroaraujo/scriptR")
```

## Example

The `scriptR` package currently contains three functions:

-   `parse_script`: creates an R6 object with some datasets available via the `$` operator.

    -   `$code` has a modified version of what you'd get with `getParseData()`

    -   `$functions` has a modified version of `$code`, such that only function calls are retained.

    -   `$pkg_search` contains the `search()` path for the libraries loaded in the scripts via `library()`.

-   `get_unused_objects`: produces the unused objects contained in a script (`$code`).

-   `get_conflicts`: produces the conflicts among packages.

This last function will work with *any* vector of installed package names.

For example:

```{r}
library(scriptR)

get_conflicts(c("network", "igraph", "dplyr"))
```

More examples:

```{r}
url <- "https://raw.githubusercontent.com/acastroaraujo/ccc/master/data-raw/04-docterms.R"

out <- parse_script(url)
out
dplyr::glimpse(out$code)
dplyr::glimpse(out$functions)
out$pkg_search
```

It's then very easy to work with these datasets.

Last example:

```{r, message=FALSE}
library(dplyr)
pkg_df <- out$functions |>
  count(f, pkg, sort = TRUE)

pkg_df <- pkg_df |>
  group_by(pkg) |>
  summarize(
    n_functions = length(pkg),
    n = sum(n)
  ) |>
  arrange(n_functions)

## NA in this example means that the pkg was specified via the :: operator
## probably a good a idea to change this
pkg_df 
```

This is also when we would use the other `scriptR` functions:

```{r}
get_unused_objs(out$code)

get_conflicts(out$pkg_search) |> 
  filter(f %in% unique(out$functions$f)) |> 
  select_if(\(x) any(x == 1 | class(x) == "character"))
```
